### 2020-04-28 README.Rmd
Update results

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
piggyback::pb_download("las_top.Rds")
las_top = readRDS("las_top.Rds")
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
```

# tempCycleways

@@

@@

```{r cycling}
# Aim: identify wide roads that have high cycling potential

# input data --------------------------------------------------------------

up = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-prep/Leeds/osm-lines.Rds"
roads = readRDS(url(up))
# names(roads)
# summary(roads$width)
wide_potential1 = roads %>% filter(width > 10, pct.dutch > 100)
wide_potential2 = roads %>% filter(
  lanes.forward > 1 |
  lanes.backward > 1,
  pct.dutch > 50)
mapview::mapview(wide_potential2)

# # relationship between cycling and 2 way ----------------------------------
# cor(roads$lanes.forward, roads$pct.census) # there is a small correlation
# cor(roads$lanes.forward, roads$pct.dutch) # larger for go dutch scenario
# cor(roads$width, roads$pct.census, use = "complete.obs") # also a positive correlation
# plot(roads$width, roads$lanes.forward + roads$lanes.backward)
#

# out-takes ---------------------------------------------------------------

# u = "https://github.com/cyipt/cyipt-bigdata/raw/master/osm-clean/Leeds/osm-lines.Rds"
# osm_lines = readRDS(url(u))
# names(osm_lines)
# plot(osm_lines) # long time to plot...
# 
# uz = "https://github.com/cyipt/cyipt-bigdata/raw/master/forDB/roads.zip"
# d = file.path(tempdir(), "roads.zip")
# download.file(uz, d)
# r = readr::read_csv(d)
# head(r$elevation)

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
piggyback::pb_download("las_top.Rds")
las_top = readRDS("las_top.Rds")
rsf = readRDS("rsf_grouped_long.Rds")
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
```

```{r, eval=FALSE}
# general analysis of data
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  ! grepl(pattern = "motorway", highway)
  ) 
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")

rsf = readRDS("rsf_spare_line.Rds")
summary(rsf$length)
unique(rsf$region)
head(rsf$name)
rsf %>% 
  select(calcwidthnow) %>% 
  sf::st_drop_geometry() %>%
  group_by(calcwidthnow) %>% 
  summarise(n = n()) %>% 
  filter(n > 500)
wide_potential1 = rsf %>% filter(width > 10, pct.dutch > 100)
wide_potential2 = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  pctdutch > 50)
# mapview::mapview(wide_potential2) # very patchy
rsf_grouped = rsf %>% 
  group_by(name, ref, highway, region) %>% 
  summarise(pctgov = mean(pctgov)) %>% 
  ungroup()

rsf_grouped$length = sf::st_length(rsf_grouped) %>% as.numeric()
summary(rsf_grouped$length)
rsf_grouped_long = rsf_grouped %>% filter(length > 100)
# mapview::mapview(rsf_grouped_long)
rsf_grouped_long %>%
  st_drop_geometry() %>% 
  arrange(desc(pctgov)) %>%
  group_by(region) %>% 
  slice(1:10) 
tm_shape(rsf_grouped_long) + tm_lines("pctgov", lwd = 3, palette = "viridis")  
saveRDS(rsf_grouped_long, "rsf_grouped_long.Rds")
```

# Data analysis to support temporary cycleways

@@

```{r}
roads = rsf %>% filter(region == "London", pctgov > 500)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(12, 13)) + tm_scale_bar()
```

The top 10 roads:

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()

roads_top %>%
  st_drop_geometry() %>% 
  knitr::kable(digits = 0)
```

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

The top 10 roads:

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()

roads_top %>%
  st_drop_geometry() %>% 
  knitr::kable(digits = 0)
```

# Birmingham

```{r}
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

The top 10 roads:

```{r}
roads_top = roads %>%
  filter(length > 500) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()

roads_top %>%
  st_drop_geometry() %>% 
  knitr::kable(digits = 0)
```
